Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
tigher spacing for the tasks list
What we want feedback on.

\begin{itemize}
\item Do a Google web search.
\item Watch a YouTube video.
\item Find the Amazon best-selling books.
\item Find Yahoo's exchange rate between dollars and euros.
\item Read the Wikipedia featured article.
\item Find the Twitter trending topics.
\item Find directions on Bing Maps.
\end{itemize}

@@

\noindent {\bfseries 1. testing the pluggable transports} blah explain ourselves.

\noindent {\bfseries 2. censorship environments} blah explain ourselves.

\noindent {\bfseries 3. list of tasks} blah explain ourselves.

\noindent {\bfseries 4. general design feedback} (size, recruitment pool --ie general or journalists) blah explain ourselves.

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Do a Google web search.
\item Watch a YouTube video.
\item Find the Amazon best-selling books.
\item Find Yahoo's exchange rate between dollars and euros.
\item Read the Wikipedia featured article.
\item Find the Twitter trending topics.
\item Find directions on Bing Maps.
\end{itemize}

@@

During the question-and-answer session,
we will be especially interested in soliciting feedback
on these topics:

{\bfseries Targeting specific pluggable transports.}
Some pluggable transports work in censorship environments
where others don't.
Also, some of them require additional information
(like bridge addresses) before they can work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports?

{\bfseries Censorship environments.}
Our proposed censorship environments are informed
by real-world censors.
What other representative environments
should be tested?

{\bfseries Browsing tasks.}
Circumvention is broader than the stereotypical
``dissident blogger'' use case.
We have invented some tasks that use some of the
most popular web sites.
What other browsing tasks make sense to test?

{\bfseries Experimental design.}
Our initial study was aimed at journalists.
We plan to remove this restriction in order
to have a larger participant population.
We aim to make our results reproducible by publishing
our software and firewall configurations.
